A Variant of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2015-10-06 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Improve a discussion sentence

If G\"odel's ontological proof is abstractly analyzed, then we are proving a restricted modal collapse, which applies to one specific formula, the existence of a God-like being. The interest in the proof naturally decreases if a consequence of the axiomatization is a modal collapse for \emph{all} formulas. Therefore, an improvement would be obtained if the modal collapse was limited only to the property of being god-like or at least to a restricted collection of properties. Several solutions to the problem of modal collapse have been proposed.

>>>>

In G\"odel's ontological proof, we are proving a restricted modal collapse, which applies to one specific formula, the existence of a God-like being. The interest in the proof naturally decreases if a consequence of the axiomatization is a modal collapse for \emph{all} formulas. Therefore, an improvement would be obtained if the modal collapse was limited only to the property of being god-like or at least to a restricted collection of properties. Several solutions to the problem of modal collapse have been proposed.
